UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-10 files/paper/paper.tex
updates

\subsection{Network Architecture and Training Details}
We use an encoder-decoder network similar to the work of \cite{isola2016image}, in which our generator is
structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.

``U-Net''

L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.

>>>>

\subsection{Network Architecture and Training Details}
We use an encoder-decoder network similar to the work of \cite{isola2016image}, in which our generator is
structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
Encoder-decoder networks continuously downsample (encode) the input to a lower dimensional embedding, in which this embedding is then
upsampled (decode) to reconstruct the image. The advantage of using a ``U-Net'' comes from explicitly preserving spatial
dependencies produced by the encoder, as opposed to relying on the embedding to contain all of the information. This
is done by the addition of ``skip connections'', which concatenate the activations produced from a convolution
layer $i$ in the encoder to the input of a transpose convolution layer $n-i+1$ in the decoder, where $n$ is the
total number of layers in the network.

Our generator network can be viewed as two subnetworks, an encoder and a decoder. Each convolutional layer in the encoder and decoder
has a kernel size of 4 and stride 2. Following \cite{radford2015unsupervised}, we use Batch Normalization \cite{pmlr-v37-ioffe15}
except for the last layer of the decoder.

\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
